### 2021-03-06 paper_1.tex
CBSP
LLFE

The research of the possible potential positions, of the salient structures, is 
carried out with the help of the contour-based spatial prior (CBSP) process, 
which uses the contours detected in a non-selective path. At the same time, 
in the selective path, the local characteristics concerning color, luminance 
and texture are extracted. The information obtained from the CBSP is inserted 
into the Bayesian framework for the prediction of the salient structure. 
Finally, the output of the Bayesian framework will represent the salient structure 
which will be improved through an iterative procedure applied on the 
CBSP process. The flowchart of the proposed method is summarized in Fig. 1.

\subsubsection{\emph{Contour-Based Spatial Prior (CBSP)}}

>>>>

The research of the possible potential positions, of the salient structures, is 
carried out with the help of the contour-based spatial prior (CBSP) process, 
which uses the contours detected in a non-selective path. At the same time, 
in the selective path, the local characteristics concerning color, luminance 
and texture are extracted. The information obtained from the CBSP is inserted 
into the Bayesian framework for the prediction of the salient structure. 
Finally, the output of the Bayesian framework will represent the salient structure 
which will be improved through an iterative procedure applied on the 
CBSP process. The flowchart of the proposed method is summarized in Fig. \ref{fid: flowchart}.

\subsubsection{\emph{Contour-Based Spatial Prior (CBSP)}}
\begin{figure}[htbp]
    \centering
    \includegraphics[width = 0.8\linewidth]{images/CBSP.png}
    \centering
    \caption{CBSP reconstruction}
    \label{fid: CBSP}
\end{figure}
Within the non-selective path, the crucial operation is to calculate the 
approximate spatial weights of salience based on the distribution of the previously 
detected contours. In this path there is the problem of determining 
the local information of each object. The solution to the problem is based 
on an operation that fills the regions delimited by these contours. A very 
efficient method proposed in \cite{07478155} result is used for the extraction of the contours.
An example of CBSP reconstruction is shown in Fig. \ref{fid: CBSP}. Each pixel 
has a direction represented by a radius $ d_r $ which is equal to $d_r = min (H, W) / 3$, where 
\emph{H} and \emph{W} correspondingly indicate the width and height of the entire image.
The diameter divides the circle into two parts where, on each of these, for 
each pixel belonging to the edge, the average response of the edge (AER) will 
be calculated. This calculation is useful in deciding which of the two halves 
will belong to the salient region. Each spatial weight of salience is denoted 
by $ S_e $, while the added bias is denoted by $ S_c $ and both are normalized in the 
range of [0,1]. The value, which in turn will be normalized, of CBSP is given by: $$ S_w = S_e + S_c $$

\subsubsection{Low-Level Feature Extraction}
Features such as color (rgb), luminance (flum) and texture are extracted in 
parallel. There are complicated regions in a texture that can be represented. 
For this purpose, the texture channel ($ {f_{ed}} $)  has been introduced, which is 
useful to better represent the salient regions using the contour density (ED). 
The texture channel is calculated by using an 11x11 filter that smooths the 
edges.
